### 2024-02-05 docs/results/seasonality.qmd
Reformat the report
Plot ACF/PACF and seasonal pattern of detrended data, closes #7, closes #8, CU-86cuhtqv9, CU-86cuhtqz6, CU-86cuhtqmg

---
knitr:
  opts_chunk:
    fig.width: 12
    fig.height: 6
---

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

@@

### Time-series on a weekly interval

```{r, fig.width = 14}

@@

@@

## Autocorrelation plots

@@

tar_read(plt_acf_diff_month)[[1]]
tar_read(plt_pacf_diff_month)[[1]]

@@

tar_read(plt_acf_diff_month)[[3]]
tar_read(plt_pacf_diff_month)[[3]]

@@

tar_read(plt_acf_diff_month)[[4]]
tar_read(plt_pacf_diff_month)[[4]]

@@

\KOMAoptions{paper=portrait,pagesize}
\recalctypearea

## Polar Plots

### Number of claim

tar_read(plt_polar_n_claim)

### Claim-to-patient ratio

tar_read(plt_polar_claim2patient)

### Eigenvector centrality

tar_read(plt_polar_eigen)

>>>>

---
knitr:
  opts_chunk:
    fig.width: 14
    fig.height: 8
---

{{< pagebreak >}}
\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

@@

### Differenced time-series on a daily interval

tar_read(plt_dot_diff_day)[-5]

### Differenced time-series on a weekly interval

@@

### Differenced time-series interval on a monthly interval

tar_read(plt_dot_diff_month)[-5]

@@

## Autocorrelation periodic plots

### Exploring seasonality within the number of medication claims (day) {#sec-nclaim-day}

tar_read(plt_period_day)[[1]]
tar_read(plt_acf_diff_day)[[1]]
tar_read(plt_pacf_diff_day)[[1]]

### Exploring seasonality within the number of patients (day) {#sec-npat-day}

tar_read(plt_period_day)[[2]]
tar_read(plt_acf_diff_day)[[2]]
tar_read(plt_pacf_diff_day)[[2]]

### Exploring seasonality within the claim-to-patient ratio (day) {#sec-ratio-day}

tar_read(plt_period_day)[[3]]
tar_read(plt_acf_diff_day)[[3]]
tar_read(plt_pacf_diff_day)[[3]]

### Exploring seasonality within the eigenvector centrality (day) {#sec-eigen-day}

tar_read(plt_period_day)[[4]]
tar_read(plt_acf_diff_day)[[4]]
tar_read(plt_pacf_diff_day)[[4]]

### Exploring seasonality within the number of medication claims (week) {#sec-nclaim-week}

tar_read(plt_period_week)[[1]]
tar_read(plt_acf_diff_week)[[1]]
tar_read(plt_pacf_diff_week)[[1]]

### Exploring seasonality within the number of patients (week) {#sec-npat-week}

tar_read(plt_period_week)[[2]]
tar_read(plt_acf_diff_week)[[2]]
tar_read(plt_pacf_diff_week)[[2]]

### Exploring seasonality within the claim-to-patient ratio (week) {#sec-ratio-week}

tar_read(plt_period_week)[[3]]
tar_read(plt_acf_diff_week)[[3]]
tar_read(plt_pacf_diff_week)[[3]]

### Exploring seasonality within the eigenvector centrality (week) {#sec-eigen-week}

tar_read(plt_period_week)[[4]]
tar_read(plt_acf_diff_week)[[4]]
tar_read(plt_pacf_diff_week)[[4]]

@@

tar_read(plt_period_month)[[1]]
tar_read(plt_acf_diff_month)[[1]]
tar_read(plt_pacf_diff_month)[[1]]

### Exploring seasonality within the number of patients (month) {#sec-npat-month}

tar_read(plt_period_month)[[2]]
tar_read(plt_acf_diff_month)[[2]]
tar_read(plt_pacf_diff_month)[[2]]

@@

tar_read(plt_period_month)[[3]]
tar_read(plt_acf_diff_month)[[3]]
tar_read(plt_pacf_diff_month)[[3]]

@@

tar_read(plt_period_month)[[4]]
tar_read(plt_acf_diff_month)[[4]]
tar_read(plt_pacf_diff_month)[[4]]

@@
